`r params$project_title`

### 2020-10-30 reports/rmarkdown/00_knit_all_reports.Rmd
adds integrated analysis

```{r, echo = T}
rmarkdown::render(input = paste0(PATH,"/reports/rmarkdown/02_data_quality_control.Rmd"),
                  output_format = "pdf_document")
```

@@

for(i in dataset_names){
  rmarkdown::render(input = paste0(PATH,"/reports/rmarkdown/03_individual_reports.Rmd"),
                    output_format = "pdf_document",
                    params = list(dataset=i),
                    output_file = paste0(PATH,"/reports/rmarkdown/report_",sub(".csv","",i)))
}
```

>>>>

```{r, echo = T}
rmarkdown::render(input = paste0(PATH,"/reports/rmarkdown/02b_data_quality_control.Rmd"),
                  output_format = "pdf_document")
```

@@

for(i in dataset_names){
  rmarkdown::render(input = paste0(PATH,"/reports/rmarkdown/02_individual_reports.Rmd"),
                    output_format = "pdf_document",
                    params = list(dataset=i),
                    output_file = paste0(PATH,"/reports/rmarkdown/report_",sub(".csv","",i)))
}
```

```{r, echo = T}
rmarkdown::render(input = paste0(PATH,"/reports/rmarkdown/03_integrated_datasets.Rmd"),
                  output_format = "pdf_document")
```

### 2020-10-30 reports/rmarkdown/02_individual_reports.Rmd
adds integrated analysis

#Graph construction  
fct <- .25 # FC threshold for differential expression
pvt <- 0.05 # Pvalue threshold for differential expression
min_pct <- .1 # minimun level of detected bacteria in each sample group

#dataset use
dataset_use <- 3
```

>>>>

#Graph construction  
fct <- .25 # FC threshold for differential expression
pvt <- 0.05 # Pvalue threshold for differential expression
min_pct <- .1 # minimun level of detected bacteria in each sample group
```
